\documentclass[12pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{setspace}

\doublespacing

\begin{document}

\section*{Introduction}

\subsection*{Statement of Purpose}
The objective behind this study is to better understand how adults in Manizales, Colombia view the current bike sharing systems offered.
This study attempts to determine which certain factors such as safety, efficiency, and reliability,
the people of Manizales consider when assessing the quality of the current bike sharing systems. Additionally, this study seeks to identify how individuals predict
possible improvements relating to infrastructure, technology, and safety to the current bike sharing systems might 
impact their use and view of them in the future.
\subsection*{Research Question}
Which certain factors such as safety, efficiency, and reliability influence how 
adults view and assess the current bike sharing systems offered CityBioBike and Oficina de la Bici - Manizales in Manizales, Colombia? 
How do they perceive potential improvements relating to infrastructure, technology, and safety
to the current bike sharing systems impacting their use and view of them in the future?

\subsection*{Subproblems}
\begin{enumerate}
    \item How do current users view the safety, efficiency, and reliability of the current bike sharing systems' infrastructure and initiatives?
    \item To what extent does the safety of the current bike sharing infrastructure and initiatives negatively influence how an
    individual views and assesses it?
    \item To what extent does the efficiency of the current bike sharing infrastructure negatively influence how an
    individual views and assess it?
    \item To what extent does the reliability of the current bike sharing infrastructure negatively influence how an
    individual views and assess it?
    \item What factors are most valued when an individual evalutes the potential benefit of future improvements to the bike sharing system?
\end{enumerate}



\end{document}